---
title: "Covid-19 Case Growth"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(dplyr)
library(readr)
library(ggpubr)
library(ggplot2)
library(RcppRoll)
library(plotly)
source('functions.R')
```

```{r get_data, include=FALSE}

county_data_nyt <<- get_county_nyt()
county_data_virginia <<- get_virginia()
county_pop <<- read_csv('2019_county_populations.csv')

county_data_nyt <<- merge_county_pop(county_data_nyt,county_pop)
state_data_nyt <<- get_state_data_nyt()
state_data_covid_tracking <<- get_state_data_covid_tracking()

max_date <- (county_data_nyt$date %>% na.omit %>% max)
default_bin <- 7
```

NYT Data Last updated at *`r max_date`*. Datasets loaded directly from [NY Times](https://github.com/nytimes/covid-19-data) for county data. State data is either NYT or [Covid Tracking](https://covidtracking.com/api).

For simplicity, I've turned off using county-level data from the [Virginia Department of Health](http://www.vdh.virginia.gov/coronavirus/). The NY Times data set has matched this exactly for quite some time.

You can select multiple states for the State Level view, and county view. Multiple states must be picked first to populate the list of County,State pairs.



# Covid 19 Plots {.tabset}

## Case Growth Plots {.tabset}


```{r echo=FALSE}


inputPanel(
  selectInput("state", label = "State",
              choices = state_data_nyt$state %>% unique %>% sort, selected = 'Virginia',multiple=TRUE),
  
  sliderInput("bins", label = "Days for Rolling Average",
              min = 1, max = 14, value = 7, step = 1)
  
  
 
  )



```

### County Level

```{r echo=FALSE}

renderUI({
  
      selected_state <- input$state[1]

  
    county_data <<- county_data_nyt
  
  
      inputPanel(
  
  
  selectInput("county", label = "County",
              choices = (county_data %>% filter(state %in% input$state))$state_county %>% unique %>% sort, selected = 'Henrico, Virginia',multiple=TRUE)
  

)

})

renderPlotly({
  

    county_data <<- county_data_nyt


shiny::validate(need(input$state,message="Please wait.."))
shiny::validate(need(county_data,message="Please wait.."))
shiny::validate(need(input$bins,message="Please wait.."))
shiny::validate(need(input$county,message="Please wait.."))


  if (length(input$county) == 1) {
    p <- plot_county2(county_data, input$county, input$state[1], input$bins)
  } else if (length(input$county) > 1) {
    p <- plot_county_per_capita(county_data,input$county,input$bins)
  }
  
  shiny::validate(need(p,message="Please wait.."))
  ggplotly(p,height=500) %>% layout(legend = list(orientation = "v", x = 0.1, y = .8))
  })

```

This text appears to be getting covered up.

### State Level
``` {r state plots, echo=FALSE}

inputPanel(
  selectInput("data_source", label = "State Source",
              choices = c("New York Times"="nyt","Covid Tracking"='covid_tracking'), selected = 'nyt'))

renderPlotly({
  if (input$data_source == 'nyt') {
    state_data <- state_data_nyt
  } else {
    state_data <- state_data_covid_tracking
  }
    
    
    if (length(input$state) > 1) {
          pp <- plot_compare_states(state_data, input$state, input$bins)

    } else {
      pp <- plot_state2(state_data, input$state, input$bins)

    }
  
    ggplotly(pp,height=500) %>% layout(legend = list(orientation = "v", x = 0.1, y = .8))

})

```

## About

Covid Tracking and the New York Times have significantly different total counts for some states, which can lead to very different case growth plots. Covid Tracking updates more frequently, but I am using the NYT as the default data source for state plots.

Covid Tracking includes a `positiveIncrease` column. For the NY Times data, this column is computed with a simple `mutate(case_growth = cases - lag(cases))` after sorting by date.

I have looked for alternatives to county-level data from the [NY Times github](https://github.com/nytimes/covid-19-data). I haven't found any useful sources yet. It is unclear where the [John Hopkins](https://github.com/CSSEGISandData/COVID-19) county data comes from, and the data files that do exist there have a difficult to parse format, with the [values in different columns for different dates](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv)). If I can find another county data source, I will try to add it.

For state population I'm using POPESTIMATE19 from various CSV files available from the US Census. [US Census](https://www.census.gov/newsroom/press-kits/2019/national-state-estimates.html)

For county level I resolved UTF-8 issues (thanks BBedit!) with this [data set with FIPS codes](https://github.com/prairie-guy/2019-State-and-County-Population-with-FIPS-key) and use that for merging.

