---
title: "County Graph New Covid-19 Cases"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(dplyr)
library(readr)
library(ggpubr)
library(ggplot2)
library(RcppRoll)
library(plotly)
source('functions.R')
```

```{r get_data, include=FALSE}


county_data <- read_csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv"))
county_data <- county_data %>% group_by(county,state) %>% mutate(case_growth = cases - lag(cases))

state_data_nyt <- get_state_data_nyt()
state_data_covid_tracking <- get_state_data_covid_tracking()

max_date <- (as.Date(county_data$date) %>% na.omit %>% max)
default_bin <- 7
```

NYT Data Last updated at *`r max_date`*. Datasets loaded directly from [NY Times](https://github.com/nytimes/covid-19-data) for county data. State data is either NYT or [Covid Tracking](https://covidtracking.com/api).

Covid Tracking and the New York Times have significantly different total counts for some states, which can lead to very different case growth plots. Covid Tracking updates more frequently, but I am defaulting to NYT for state plots for the time being.

```{r define_functions, echo=FALSE}

plot_state <- function(state_data,my_state,roll_days) {

  plot_data <- state_data %>% filter(state==my_state) %>% select (case_growth,state,date) %>% na.omit
 plot_data <- plot_data[order(plot_data$date),]
 plot_data <- plot_data %>% mutate(rolled_average_case_count = roll_mean(case_growth,roll_days,na.rm=TRUE,align ='right',fill=NA)) %>% select(date,rolled_average_case_count) %>% na.omit
  ggbarplot(plot_data,'date','rolled_average_case_count', fill="dark blue",ggtheme = theme_minimal(),ylab='New Cases',xlab='Date',title=paste("All",my_state)) + theme(text = element_text(size=12))
  }

plot_county_roll <- function(my_county,my_state,roll_days) {
    plot_data <- county_data %>% filter(county == my_county & state==my_state) %>% na.omit
    
    plot_data <- plot_data %>% mutate(rolled_average_case_count = roll_mean(case_growth,roll_days,na.rm=TRUE,align ='right',fill=NA)) %>% na.omit
    
    ggbarplot(plot_data,'date','rolled_average_case_count', fill="light blue",ggtheme = theme_minimal(),ylab='New Cases',xlab='Date',title = paste(my_county,my_state,sep=", ") ) + theme(text = element_text(size=12))
}
```

# Covid 19 Plots {.tabset}

## Case Growth Plots {.tabset}


```{r echo=FALSE}

inputPanel(
  selectInput("data_source", label = "State Data Source",
              choices = c("New York Times"="nyt","Covid Tracking"='covid_tracking'), selected = 'nyt'))



inputPanel(
  selectInput("state", label = "State",
              choices = county_data$state %>% unique %>% sort, selected = 'Virginia'),
  
  sliderInput("bins", label = "days to bin",
              min = 1, max = 14, value = 7, step = 1)
  )

renderUI({


selected_state <- input$state

inputPanel(
  selectInput("county", label = "County",
              choices = (county_data %>% filter(state == selected_state))$county %>% unique %>% sort, selected = 'Henrico')
)
})

```

### County Level

```{r echo=FALSE}

renderPlotly({
  shiny::validate(need(input$county,message="Please wait.."))
plot_county_roll(input$county,input$state,input$bins)
})

```

### State Level
``` {r state plots, echo=FALSE}



renderPlotly({
    if (input$data_source == 'nyt') {
    state_data <- state_data_nyt
  } else {
    state_data <- state_data_covid_tracking
  }
  
plot_state(state_data,input$state,input$bins)
})

```

## State Per Capita Comparisons

Work in Progress

